<!-- R Commander Markdown Template -->
  
  Replace with Main Title
=======================
  
  ### Savanna
  
  ### `r as.character(Sys.Date())`
  
  ```{r echo=FALSE}
# include this code chunk as-is to set options
knitr::opts_chunk$set(comment=NA, prompt=TRUE, out.width=750, fig.height=8, fig.width=8)
library(Rcmdr)
library(car)
library(RcmdrMisc)
```
## Please modify this section of the code to change to your own directory. Make absolutely sure that you have all 
#of the relevant associated data files in your directory as well.

```{r}
setwd("C:/Users/Savanna/Documents/1NewRDirectory")
```




```{r}
BarrowPlantSpecies <- read.csv("BarrowPlantSpecies.csv")
```


```{r}
str(BarrowPlantSpecies)
```

```{r}
PlantChemistry <- read.csv("BarrowPlantChemistry.csv")
```


```{r}
str(PlantChemistry)
```


```{r}
BarrowPlantChemistry <- read.csv("BarrowPlantChemistry.csv")
```


```{r}
str(BarrowPlantChemistry)
```

#Converting to dataframes for analyses

```{r}
BarrowPlantSpecies1 <- data.frame(BarrowPlantSpecies)
```

```{r}
BarrowPlantChemistry1 <- data.frame(BarrowPlantChemistry)
```

#Running the first of several analyses to determine biodiversity levels in different concentrations of specific elements,
#as well as in different pH levels for the Barrow data

```{r}
BarrowPlantChemistry1$pH_level <- as.factor(BarrowPlantChemistry1$pH_level)
```


```{r}
Barrow.pH <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'pH_level',
                       scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.pH)
```

```{r}
Barrow.pH
```

```{r}
BarrowPlantChemistry1$Al2O3 <- as.factor(BarrowPlantChemistry1$Al2O3)
```


```{r}
BarrowAl2O3 <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'Al2O3',
                         scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(BarrowAl2O3)
```

```{r}
BarrowAl2O3
```

```{r}
BarrowPlantChemistry1$MgO <- as.factor(BarrowPlantChemistry1$MgO)
```


```{r}
Barrow.MgO <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'MgO',
                        scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.MgO)
```

```{r}
Barrow.MgO
```


```{r}
BarrowPlantChemistry1$CaO <- as.factor(BarrowPlantChemistry1$CaO)
```

```{r}
Barrow.CaO <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'CaO',
                        scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.CaO)
```

```{r}
Barrow.CaO
```

```{r}
BarrowPlantChemistry1$Fe2O3 <- as.factor(BarrowPlantChemistry1$Fe2O3)
```

```{r}
Barrow.Fe2O3 <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'Fe2O3',
                          scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.Fe2O3)
```

```{r}
Barrow.Fe2O3
```

```{r}
BarrowPlantChemistry1$Na2O <- as.factor(BarrowPlantChemistry1$Na2O)
```

```{r}
Barrow.Na2O <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'Na2O',
                         scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.Na2O)
```

```{r}
Barrow.Na2O
```

```{r}
BarrowPlantChemistry1$K2O <- as.factor(BarrowPlantChemistry1$K2O)
```

```{r}
Barrow.K2O <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'K2O',
                        scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.K2O)
```

```{r}
Barrow.K2O
```

```{r}
BarrowPlantChemistry1$Cr2O3 <- as.factor(BarrowPlantChemistry1$Cr2O3)
```

```{r}
Barrow.Cr2O3 <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'Cr2O3',
                          scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.Cr2O3)
```

```{r}
Barrow.Cr2O3
```

```{r}
BarrowPlantChemistry1$TiO2 <- as.factor(BarrowPlantChemistry1$TiO2)
```

```{r}
Barrow.TiO2 <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'TiO2',
                         scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.TiO2)
```

```{r}
Barrow.TiO2
```

```{r}
BarrowPlantChemistry1$MnO <- as.factor(BarrowPlantChemistry1$MnO)
```

```{r}
Barrow.MnO <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'MnO',
                        scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.MnO)
```

```{r}
Barrow.MnO
```

```{r}
BarrowPlantChemistry1$P2O5 <- as.factor(BarrowPlantChemistry1$P2O5)
```

```{r}
Barrow.P2O5 <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'P2O5',
                         scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.P2O5)
```

```{r}
Barrow.P2O5
```

```{r}
BarrowPlantChemistry1$SrO <- as.factor(BarrowPlantChemistry1$SrO)
```

```{r}
Barrow.SrO <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'SrO',
                        scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.SrO)
```

```{r}
Barrow.SrO
```

```{r}
BarrowPlantChemistry1$BaO <- as.factor(BarrowPlantChemistry1$BaO)
```

```{r}
Barrow.BaO <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'BaO',
                        scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.BaO)
```

```{r}
Barrow.BaO
```

```{r}
BarrowPlantChemistry1$Al <- as.factor(BarrowPlantChemistry1$Al)
```

```{r}
Barrow.Al <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'Al',
                       scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.Al)
```

```{r}
Barrow.Al
```

```{r}
BarrowPlantChemistry1$As <- as.factor(BarrowPlantChemistry1$As)
```

```{r}
Barrow.As <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'As',
                       scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.As)
```

```{r}
Barrow.As
```

```{r}
BarrowPlantChemistry1$Co <- as.factor(BarrowPlantChemistry1$Co)
```

```{r}
Barrow.Co <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'Co',
                       scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.Co)
```

```{r}
Barrow.Co
```

```{r}
BarrowPlantChemistry1$Pb <- as.factor(BarrowPlantChemistry1$Pb)
```

```{r}
Barrow.Pb <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'Pb',
                       scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.Pb)
```

```{r}
Barrow.Pb
```

```{r}
BarrowPlantChemistry1$S <- as.factor(BarrowPlantChemistry1$S)
```

```{r}
Barrow.S <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'S',
                      scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.S)
```

```{r}
Barrow.S
```

```{r}
BarrowPlantChemistry1$V <- as.factor(BarrowPlantChemistry1$V)
```

```{r}
Barrow.V <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'V',
                      scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.V)
```

```{r}
Barrow.V
```